---
title: "Dyanmic Assignment"
author: "GABA FOLLY NAPO"
format: html
editor: visual
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```



```{r,echo=TRUE, warning=FALSE}
library(ggplot2)
library(plotly)
library(htmlwidgets)
library(dygraphs)
library(dplyr)
library(lubridate, warn.conflicts = FALSE)
library(anytime)
library(xts)
```


*Description of the data and data source*

For this assignment we use the data produes by the National Association of Realtors (NAR). NAR produces housing statistics on the national, regional, and metro-market level where data is available. we use the national historical data (view US data) on https://www.realtor.com/research/data/

*what you want to convey in the figure*

Through the figure we want to show how the median listing price and the median listing square feet change monthly from 2017 to 2022 in the united states.

*Functionality and formatting put into the figure and why*

package *dygraphs* is used to create an interactive graph. the functionality *dyRangeSelector* with no specification of window and *dyOptions* (stackedGraph =TRUE) to stack series on top of one another rather than drawing them independently. we only formatting the date in the standard form *yyyy-mm-dd* by using `anydate` in the package *anytime* and also as.Date to have the class equal to date.

Those functionality and formatting were used, because we have and interactive graph,
we can mouse over to highlight individual values


*Upload Date and formatting the date*

```{r,warning=FALSE}
library(tidyverse)
house=read.csv("C:/Users/L/OneDrive/Bureau/STAA 566/Dynamic Figure/RDC_Inventory_Core_Metrics_Country_History.csv",header = TRUE)
house=house%>% rename(Date=month_date_yyyymm)
house$Date=anydate(house$Date)
house$Date=as.Date(house$Date,"%y-%m-%d")
house=house %>% drop_na()
class(house$Date)
House=house %>%
select(Date, median_listing_price, median_square_feet)
head(House)
```
*Make an `xts` object and index of times*

```{r}
# make an xts object
xts_House <- xts::xts(x= house %>% select(median_listing_price, median_square_feet),
                      order.by = house %>% pull(Date)) # x axis
class(xts_House)
# index of the time
head(attr(xts_House,"index"))
```

*Data visualization (make a Figure)*

```{r}
graph <- dygraph(xts_House, main = "Evolution of the median (listing price & square feet) from 2017 to 2020") %>%
dySeries("median_listing_price", label = "Median listing price") %>%
dySeries("median_square_feet", label = "Median square feet") %>%
dyRangeSelector() %>%
dyOptions(stackedGraph = TRUE)
```


*Save figure as PDF*

```{r}
pdf("interaction_assignmnent.pdf", height=4, width=6)
dev.off()
```

*Display Figure in HTLM*

```{r}
graph
```

